Distrivia: A Distributed Trivia Game

### 2011-05-12 papers/phase-three/paper.tex
Paper: Proper citations and editted images.
Paper: Add Sam's lessons learned paragraph

\title{ Distrivia: A Distributed Trivia Game }
\numberofauthors{3}
\author{
\alignauthor
Brian Gianforcaro \\
   	\affaddr{Rochester Institute of Technology}\\
   	\email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
   	\affaddr{Rochester Institute of Technology}\\
   	\email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
   	\affaddr{Rochester Institute of Technology}\\
   	\email{srm2997@rit.edu}
}
\maketitle

@@

\begin{figure}[h!]
   \includegraphics[scale=0.21]{web_join.png}
   \includegraphics[scale=0.21]{web_leader.png}
   \includegraphics[scale=0.21]{web_round.png}
   \caption{Web Client User Interface}
\end{figure}

@@

\section{Future Work}
For future work on this system, we've thought of adding a few new features that would improve gameplay and diversity of the experience for the players.
We don't have have any revolutionary upgrades we'd like to perform on the server-side.
Overall, we are satisfied with the performance of the server including the reliability, response speed, and availability. The features we have contemplated adding in future work include: categories, user added content, support for more platforms, and private competition via bluetooth or local wifi.

>>>>

\title{ Distrivia: A Distributed Trivia Game }
%\numberofauthors{3}
%\author{
%\alignauthor
%Brian Gianforcaro \\
%   	\affaddr{Rochester Institute of Technology}\\
%   	\email{bjg1955@rit.edu}
%\alignauthor
%Steven Glazer \\
%   	\affaddr{Rochester Institute of Technology}\\
%   	\email{sfg6126@rit.edu}
%\alignauthor
%Samuel Milton \\
%   	\affaddr{Rochester Institute of Technology}\\
%   	\email{srm2997@rit.edu}
%}
\maketitle

@@

\begin{figure}[h!]
   \includegraphics[scale=0.24]{web_join.png}
   \includegraphics[scale=0.24]{web_leader.png}
   \includegraphics[scale=0.24]{web_round.png}
   \caption{Web Client User Interface}
\end{figure}

@@

Another lesson we learned was that we should start with a well defined API.  We
endured a lot of headaches during this project as a result of incompatible API
calls between the server and clients.  Even after we went and defined how we
wanted out API calls to work, we neglected to specifically state how they would
return some of the information.  So we continued to have problems there.  If we
had taken the time to sit down as a group in the beginning and create a well
thought-out API set, it would have greatly simplified our implementations
later.  
\section{Future Work}
For future work on this system, we've thought of adding a few new features that would improve gameplay and diversity of the experience for the players.
We don't have have any revolutionary upgrades we'd like to perform on the server-side.
Overall, we are satisfied with the performance of the server including the reliability, response speed, and availability. The features we have contemplated adding in future work include: categories, user added content, support for more platforms, and private competition via bluetooth or local wifi.
